Semantic Preserving Bijective Mappings for Representations of Special Functions between Computer Algebra Systems and Document Preparation Systems

### 2018-11-16 main.tex
Changed position of paragraph vom 6.1 to 6

\section{\Maple{} to Semantic \LaTeX{} Translator}\label{sec:backward-translation}
Instead of writing a custom \Maple{} syntax parser, we use \Maple's internal data structure to get a syntax tree of the input\footnote{In consequence, a license of \Maple{} is mandatory to perform backward translations. The translator is using the version \Maple{} 2016.}. \Maple{} allows several different input styles. The \texttt{1D} input is mainly used for programming purposes and therefore also used to perform our translations. Internally, \Maple{} uses a \gls*{dag} for syntax trees.

@@

\subsection{Automatic Changes of Inputs in Maple}\label{subsec:maple-probs}
In this section, we will discuss several techniques to get access to the parse tree of \Maple's input. The translation process from this parse tree than follows the same principle as for the forward translations.

\Maple{} evaluates inputs automatically and changes the input into an internal representation. This internal representation might look a bit different to the input. One example has already been given with \Cref{fig:internal-maple-dag}, where each summand of a sum is stored with a factor. Here is a list of all internal changes that occur for inputs.

>>>>

\section{\Maple{} to Semantic \LaTeX{} Translator}\label{sec:backward-translation}
In this section, we will discuss several techniques to get access to the parse tree of \Maple's input. The translation process from this parse tree than follows the same principle as for the forward translations.

Instead of writing a custom \Maple{} syntax parser, we use \Maple's internal data structure to get a syntax tree of the input\footnote{In consequence, a license of \Maple{} is mandatory to perform backward translations. The translator is using the version \Maple{} 2016.}. \Maple{} allows several different input styles. The \texttt{1D} input is mainly used for programming purposes and therefore also used to perform our translations. Internally, \Maple{} uses a \gls*{dag} for syntax trees.

@@

\subsection{Automatic Changes of Inputs in Maple}\label{subsec:maple-probs}
\Maple{} evaluates inputs automatically and changes the input into an internal representation. This internal representation might look a bit different to the input. One example has already been given with \Cref{fig:internal-maple-dag}, where each summand of a sum is stored with a factor. Here is a list of all internal changes that occur for inputs.
